Interisland movements and oceanic swimming of woodland caribou in Newfoundland

### 2020-05-14 paper/manuscript.Rmd
update Q1

1) How does the energetic cost or risk of swimming differ from walking on sea
ice? The cost of swimming may be lower than the risk of falling through sea ice
and drowning, so what proportion of inter-island movements are swimming events
compared to walking on ice? The presence and extent of sea ice varies annually
in our study area, and although we are unable to determine the exact timing or
duation of sea ice, we delineate on Figure 2b the timing of typical sea ice
arrival and departure.

>>>>

1) How does the energetic cost or risk of swimming differ from walking on sea
ice? The cost of swimming may be lower than the risk of falling through sea ice
and drowning, so what proportion of inter-island movements are swimming events
compared to walking on ice? The presence and extent of sea ice varies annually
in our study area and we are unable to determine the exact timing or duration of
sea ice from past years. However, we qualitatively delineate the timing of
typical sea ice arrival and departure (Figure 2B) and deduce that although the
majority of inter-island movements occur between April 1 and December 31, some
inter-island movements appear to be caribou walking on sea ice between islands.
Future research should focus on the trade-off between these types of movement.
